A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
attached

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit an
explicitly modelled hierarchical decomposition of the underlying
POMDP. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief-space to exponentially shrink the
state-space. Although we have been actively exploring
the \citeauthor{doshi08:pref_elic} approach, those exploitable
symmetries are not present in problems we consider due to the task
planning requirement.
%%
Finally, our approach is in a similar vein to {\em dual-mode}
control~\cite{cassandra96actingunder}, in our case we use a {\em
classical} planner to provide guidance for reducing entropy.

@@

There has also been much recent work on scaling offline approximate
POMDP solution procedures to medium-sized instances. Recent
contributions propose more efficient belief-point sampling
schemes~\cite{kurniawati:etal:2010,shani:etal:08}, and structured
representations with procedures that can efficiently exploit
them~\cite{brunskill:russell:2010,shani:etal:2008}. Offline domain
independent systems scale to {\em logistics} problems with $2^{22}$
states~\cite{shani:etal:2008}, taking over an hour to converge, and
around 10 seconds on average to perform each Bellman
backup. \citeauthor{brunskill:russell:2010} are able to solve problems
with as many as $10^{30}$ states, by further exploiting certain
problem features -- E.g., no actions with negative effects.
%%
Moving someway towards supporting real-time decision making, recent
online POMDP solution procedures have been developed which leverage
highly approximate value functions -- computed using an offline
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. These approaches are applicable in
relatively small problems, and can require
expensive \emph{problem-specific} offline processing in order to yield
good behaviours.
%%
A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

>>>>

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit an
explicitly modelled hierarchical decomposition of the underlying
POMDP. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief-space to exponentially shrink the
state-space. Although we have been actively exploring
the \citeauthor{doshi08:pref_elic} approach, those exploitable
symmetries are not present in problems we consider due to the task
planning requirement.
%%
Finally, our approach is in a similar vein to {\em dual-mode}
control~\cite{cassandra96actingunder}, where planning switches between
entropy and utility focuses.

%% serial planning in
%% problem determinisations underlines strategies to goal achievement,
%% and

%% in our case we use serial
%% planning in a determinisation of the underlying process to guide DT
%% sessions, which typically act to reducing entropy.

@@

There has also been much recent work on scaling offline approximate
POMDP solution procedures to medium-sized instances. Recent
contributions propose more efficient belief-point sampling
schemes~\cite{kurniawati:etal:2010,shani:etal:08}, and factored
representations with procedures that can efficiently exploit
structures in those
representations~\cite{brunskill:russell:2010,shani:etal:2008}. Offline
domain independent systems scale to {\em logistics} problems with
$2^{22}$ states~\cite{shani:etal:2008}, taking over an hour to
converge, and around 10 seconds on average to perform each Bellman
backup. \citeauthor{brunskill:russell:2010} are able to solve problems
with approximately $10^{30}$ states, by further exploiting certain
problem features -- E.g., problems where no actions with negative
effects.
%%
Moving someway towards supporting real-time decision making, recent
online POMDP solution procedures have been developed which leverage
highly approximate value functions -- computed using an offline
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. These approaches are applicable in
relatively small problems, and can require
expensive \emph{problem-specific} offline processing in order to yield
good behaviours.
%%
A {\em very} recent and promising online approach for
larger POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

Also leveraging deterministic planners in problems that feature
uncertainty, \system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009} demonstrate how conformant planning
---i.e., sequential planning in unobservable worlds--- can be modelled
as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. Most
recently this research thread has been extended to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.
